Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-09-01 ms.tex
Added acknowledgments.  Added Whalen08_Instab to bib.

J.H.W. is supported by the Hubble Fellowship etc.  The majority of the
analysis and plots were done with \texttt{yt} \citep{yt}.

>>>>

Support for this work was provided by NASA through Hubble Fellowship
grant \#120-6370 awarded by the Space Telescope Science Institute,
which is operated by the Association of Universities for Research in
Astronomy, Inc., for NASA, under contract NAS 5-26555.  J.K. was
supported by the William R. and Sara Hart Kimball Stanford Graduate
Fellowship.  Computational resources were provided by NASA/NCCS award
SMD-09-1439.  The majority of the analysis and plots were done with
\texttt{yt} \citep{yt}.
